Value-Suppressing Uncertainty Maps

### 2017-12-06 paper/figures.tex
Just In Case submitted version.
Some bibliography fixes.

\newcommand{\taskOneFig}{
	\begin{figure}
		\centering
		\includegraphics[width=0.95\columnwidth]{task1.png}
		\caption{Accuracy results for the identification experiment. For examples of each condition, see \protect\figref{fig:conditions}. Juxtaposing two univariate maps for both value and uncertainty requires an error-prone search task for identification tasks. Continuous rather than discrete bivariate maps requires an error-prone color encoding and estimation task. Discrete bivariate maps, both VSUPs and otherwise, avoid these issues. The confidence intervals are bootstrapped 95\% CIs of trimmed means.}
		\label{fig:taskOne}
	\end{figure}
}

@@

\newcommand{\taskTwoQuartiles}{
	\begin{figure}
		\centering
		\includegraphics[width=0.75\columnwidth]{exp2histogram.pdf}
		\caption{A histogram of the distribution of uncertainty across all participants guesses from the prediction experiment. For each trial, participants made 5 guesses. While participants generally favored low uncertainty in guesses, our stimuli design encouraged them to make at least some guesses with higher uncertainty. VSUPs encouraged more guesses with middling uncertainty, and discouraged highly uncertain guesses.}
		\label{fig:taskTwoQuartiles}
	\end{figure}
}
%\newcommand{\performanceFig}{
%	\begin{figure}[t]
%		\centering
%		\includegraphics[width=0.9\columnwidth]{performance.pdf}
%		\caption{
%			The number of discrete color categories in traditional bivariate color maps versus VSUPs, assuming value is encoded by the Viridis color map~\protect\cite{viridis}, and uncertainty is encoded by saturation/value (whiter values are more uncertain). Since these whiter uncertain colors are closer together in CIELAB space, and VSUPs intentionally require fewer color bins in those regions, VSUPs always have more color categories than the corresponding 2D bivariate map. The red lines denote:
%		  \textbf{1)} Theoretical 50\% JND from CIELAB specification.
%			\textbf{2)} 50\% JND from controlled lab study of Mahy et al.~\protect\cite{mahy1994evaluation}.
%			\textbf{3)} 50\% JND from Szafir et al.\protect\cite{szafir2014adapting}.
%			\textbf{4)} 50\% JND for small visual targets from Stone et al.~\protect\cite{stone2014engineering}.
%			\textbf{5)} The threshold resulting in the simplest possible (2x2) bivariate map.
%	    }
%		\label{fig:performance}
%	\end{figure}
%}

@@

>>>>

\newcommand{\taskOneFig}{
	\begin{figure}
		\centering
		\includegraphics[width=0.95\columnwidth]{task1.pdf}
		\caption{Accuracy results for the identification experiment. For examples of each condition, see \protect\figref{fig:conditions}. Juxtaposing two univariate maps for both value and uncertainty requires an error-prone search task for identification tasks. Continuous rather than discrete bivariate maps requires an error-prone color encoding and estimation task. Discrete bivariate maps, both VSUPs and otherwise, avoid these issues. The confidence intervals are bootstrapped 95\% CIs of trimmed means.}
		\label{fig:taskOne}
	\end{figure}
}

@@

\newcommand{\taskTwoQuartiles}{
	\begin{figure}
		\centering
		\includegraphics[width=0.75\columnwidth]{exp2histogram.pdf}
		\caption{Overlaid histograms of the distribution of uncertainty across all participants guesses from the prediction experiment. For each trial, participants made 5 guesses. While participants generally favored low uncertainty in guesses, our stimuli design encouraged them to make at least some guesses with higher uncertainty. VSUPs encouraged more guesses with middling uncertainty, and discouraged highly uncertain guesses.}
		\label{fig:taskTwoQuartiles}
	\end{figure}
}
%\newcommand{\performanceFig}{
%	\begin{figure}[t]
%		\centering
%		\includegraphics[width=0.9\columnwidth]{performance.pdf}
%		\caption{
%			The number of discrete color categories in traditional bivariate color maps versus VSUPs, assuming value is encoded by the Viridis color map~\protect\cite{viridis}, and uncertainty is encoded by saturation/value (whiter values are more uncertain). Since these whiter uncertain colors are closer together in CIELAB space, and VSUPs intentionally require fewer color bins in those regions, VSUPs always have more color categories than the corresponding 2D bivariate map. The red lines denote:
%		  \textbf{1)} Theoretical 50\% JND from CIELAB specification.
%			\textbf{2)} 50\% JND from controlled lab study of Mahy et al.~\protect\cite{mahy1994evaluation}.
%			\textbf{3)} 50\% JND from Szafir et al.\protect\cite{szafir2014adapting}.
%			\textbf{4)} 50\% JND for small visual targets from Stone et al.~\protect\cite{stone2014engineering}.
%			\textbf{5)} The threshold resulting in the simplest possible (2x2) bivariate map.
%	    }
%		\label{fig:performance}
%	\end{figure}
%}

@@

\newcommand{\pollFig}{
	\begin{figure}[t]
		\centering
		\includegraphics[width=\columnwidth]{polling-2d.pdf}
		\vspace{-15px}
		\caption{Polling data prior to the 2016 U.S. Presidential Election, encoded in a traditional 2D bivariate map. Many states appear to be ``leaning'' towards Clinton, even when the margin of error of the polls is quite large. The blue-red color scale that is semantically appropriate for the topic is also not isoluminant, making it difficult to see just how much uncertainty there is in states with small leads for either candidate.}
		\label{fig:polling2d}

		\centering
		\includegraphics[width=\columnwidth]{polling-vsum.pdf}
		\vspace{-15px}
		\caption{Polling data prior to the 2016 U.S. Presidential Election, encoded with a VSUP. The larger amount of color bins for high-certainty regions shows that the leads for Hillary Clinton were, in many states, quite small. The collapsing of bins as uncertainty increases dissuades viewers from making confident predictions about states where the outcome was very much in doubt. }
		\label{fig:pollingVsum}
	\end{figure}
}
